Clean spectral data

### 2021-02-25 R/clean_spectral_data.Rmd
show initial spectral plot

```{r, warning=FALSE, fig.height=16, fig.width=14, eval=FALSE}
all_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID,
             # color each facet plot based on taxonRank
             color = taxonRank)) +
  geom_path(alpha = .2) +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n',
       color = "Taxon Rank") + 
  facet_wrap(~genusSpecies
             # wrap long names
             ,labeller = label_wrap_gen(20)) + 
  scale_color_manual(values = c("#e6550d","#1c9099", "#a8ddb5")) + 
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```

>>>>

```{r, warning=FALSE, fig.height=16, fig.width=14, eval=TRUE}
all_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID,
             # color each facet plot based on taxonRank
             color = taxonRank)) +
  geom_path(alpha = .2) +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n',
       color = "Taxon Rank") + 
  facet_wrap(~genusSpecies
             # wrap long names
             ,labeller = label_wrap_gen(20)) + 
  scale_color_manual(values = c("#e6550d","#1c9099", "#a8ddb5")) + 
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```
